---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  #fig.path = "https://raw.githubusercontent.com/jannes-m/RQGIS/master/figures/",
  fig.align = "center",
  collapse = TRUE,
  eval = FALSE,
  comment = "#>",
  cache = TRUE
)
```

### Run RStudio, RQGIS, geocompr and QGIS in a Docker container

**Linux users**: Updating the Linux kernel to version 4.19 introduced an `dpkg`/`overlayfs` Docker issue.
As pointed out by this [post](https://github.com/docker/for-linux/issues/480), you can make Docker work again with the updated Linux kernel when running the following command on your shell prior to any docker command:

```{sh, eval=FALSE}
echo N | sudo tee /sys/module/overlay/parameters/metacopy
```

Then we can clone the `docker-rqgis` repository and build the corresponding image:

```{sh, eval=FALSE}
# clone the repository
git clone https://github.com/jannes-m/docker-rqgis.git
# navigate to the cloned directory
cd docker-rqgis/rqgis
# build the docker image, and name it rqgis
sudo docker build -t rqgis .  
```

Now you can start R either from the Shell...

```{r, eval=FALSE}
# start the container from the shell
docker run -it rqgis /bin/bash
# start R
R
```

... or using RStudio


```{r, eval=FALSE}
sudo docker run -e PASSWORD=pass -p 8787:8787 rqgis
```

Open [http://localhost:8787](http://localhost:8787) and use `rstudio` as username and `pass` as password.
Next, we have to attach the **RQGIS** package, and can then run **RQGIS** commands such as `qgis_session_info()`:

```{r, eval=FALSE}
library("RQGIS")
#> Loading required package: reticulate

qgis_session_info()
#> Assuming that your root path is '/usr'!
#> $qgis_version
#> [1] "2.18.25"
#> 
#> $gdal
#> [1] "2.1.2"
#> 
#> $grass6
#> [1] FALSE
#> 
#> $grass7
#> [1] "7.2.0"
#> 
#> $saga
#> [1] "2.3.1"
```
